\documentclass{letter}

\signature{Sam Whited}
\address{Atlanta, GA}

\begin{document}

\begin{letter}{Lincoln Town Office \\ PO Box 25 \\ Lincoln, NH 03251}
\opening{To whom it may concern:}

I am writing to you today to express my
displeasure at your decision to charge a
fee for computer use at the local library
located at \texttt{22 Church St}.

The purpose of a library is to facilitate
the betterment of humanity through open
access to information. This has traditionally
been accomplished through written word,
archival materials, and knowledgeable
support staff. In recent years the means of
spreading knowledge and information has
expanded to encompass the internet and other
computer services. One would not charge for
the use of a typewriter (though tape is much
more expensive than electricity) or for the
use of an encyclopedia (which cost a small
fortune to purchase in physical form, but may
be obtained freely online); the same goals
apply to the use of a computer.

The internet changed the world more than any
other invention of the past century ---
it shrank the world more than the telephone,
or even the genesis of commercial flight.
As Stewart Brand famously said, ``Information
wants to be free." You are in charge of a
library, a repository of free knowledge and
information, not an internet caf\'e; please
treat it as such. A library and, by extension,
the city or organization which empowers it
has a responsibility to all people, local
or alien, and this responsibility transcends
the boarders of your municipality. Please
consider making the library computers free
for all patrons, as is your duty.

\closing{Sincerely,}

\end{letter}
\end{document}

